Get CRediT

### 2022-10-28 RR_manuscript/Draft_RR.Rmd

After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes $\eta_i$.
The likelihood of $\eta_i$ was assumed to correspond to a normal distribution [@knight2000].
The analysis teams were entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
The standard errors $\text{se}_i$ were included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
<!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
The model did not incur any divergent transitions ($\hat{R}$ was equal or lower than 1) and the estimated sample sizes were sufficient.
<!-- TODO: add link to meta-model code -->
The code used to run the model can be found at <>.

@@

We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to follow the research protocol.
We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
<!-- TODO: mention that there were some and add info in descriptive stats section? -->

@@

The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0.1)` standard units and 95% probability.
The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.
We interpret these values in more details in the Discussion section.

@@

Figure \@ref(fig:plot-meta2), panel C, displays the coefficients for all predictors alongside their 80% and 95% credible intervals. 
The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction. 
Neither analysts' prior beliefs in the phenomenon `r report_posterior(predictors_bm_rintercepts, "prior_belief_s")`, nor their seniority in terms of years after completing their PhD `r report_posterior(predictors_bm_rintercepts, "years_from_phd_s")` seem to affect model estimates.
Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty `r report_posterior(predictors_bm_rintercepts, "all_rating_s")`. 
Interestingly, the model uniqueness, i.e. how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates `r report_posterior(predictors_bm_rintercepts, "pop_sdi_s")`.

@@

Regardless of the cause of these systematic effects, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant prediction.
This conclusion is further supported by the fact that between-team variability was lower than between-model variability.
This is an important observation when put into context of the fact that most teams submitted many different models.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher; @simmons2011false].
One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): "[T]he project's approach is too much top-down instead of bottom-up. [...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences. 
Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis. 
While this is a valid way to explore data and generate new hypotheses, it is not suitable for hypothesis testing.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate. 
The well-established solution to this problem is to apply a correction for family-wise error (i.e., alpha correction). 
However, less clear-cut degrees of freedom such as observed in the present study can not be corrected for in a straightforward way. 
If uncorrected for, these degrees of freedom can nevertheless drastically inflate the false positive rate, even if different choices are highly correlated [@roettger2019researcher]. 
Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking; @john2012measuring; @simmons2011false], while null results remain unreported [@sterling1959publication; @rosenthal1979file]. 
Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.

@@

The current results point to important barriers to the successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [@vazire2017quality; @fidler2018reproducibility].
One of the suggested paths forward is for researchers to directly replicate previous studies more often [@open2015estimating; @camerer2018evaluating].
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
Beyond a replication crisis, quantitative disciplines are going through what has been called an "inference crisis" [@rotello2015more; @starns2019assessing].
As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility.

@@

Finally, the present study focused on a particular phenomenon within the speech sciences using a speech production data set with very specific properties.
The generalizability of our findings to other disciplines, as well as to other sub-disciplines of the language sciences specifically, is, of course, limited.
We focused on quantitative analyses that require the operationalization of a multidimensional signal in an artificial elicitation situation (laboratory speech). 
While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals. 
This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods.
It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.

@@

In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis. 
When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to both different qualitative answers (i.e. is there evidence for a relationship or not) and vastly different effect magnitudes. 
This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.

>>>>

After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor in each reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes $\eta_i$.
The likelihood of $\eta_i$ was assumed to correspond to a normal distribution [@knight2000].
The analysis teams were entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
The standard errors $\text{se}_i$ were included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
<!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
The model did not incur any divergent transitions ($\hat{R}$ was not greater than 1) and the estimated sample sizes were sufficient.
<!-- TODO: add link to meta-model code -->
The code used to run the model can be found at <>.

@@

We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to follow the research protocol.
We also excluded any individual analysis that does not produce an outcome that could be interpreted as an answer to our primary question.
For a list of exlcusion criteria, see Section Descriptive statistics below.

@@

The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0)` to `r pm(x = 0.1)` standard units and 95% probability.
The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.
We interpret these values in more details in the Discussion section.

@@

We have run a model as described in Section Analytic and researcher-related predictors affecting effect sizes above.
Figure \@ref(fig:plot-meta2), panel C, displays the coefficients for all predictors alongside their 80% and 95% credible intervals.
The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction. 
Neither analysts' prior beliefs in the phenomenon `r report_posterior(predictors_bm_rintercepts, "prior_belief_s")`, nor their seniority in terms of years after completing their PhD `r report_posterior(predictors_bm_rintercepts, "years_from_phd_s")` seem to affect model estimates.
Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty `r report_posterior(predictors_bm_rintercepts, "all_rating_s")`. 
Interestingly, the model uniqueness, i.e. how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates `r report_posterior(predictors_bm_rintercepts, "pop_sdi_s")`.

@@

Regardless of the cause of these systematic effects, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant prediction.
This conclusion is further supported by the fact that between-team variability was lower than between-model variability.
This is an important observation when put into context of the fact that most teams submitted many different models.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher; @simmons2011false].
We of course are not arguing that exploratory analyses should not be employed.
Rather, we simply want to point out that if the theoretical underpinnings of the field were much clearer, different teams would have converged towards a limited set of analyses despite of a less specific research question.

In relation to this aspect, one team coordinator decided to drop out of the project because of its approach being too top-down.
The coordinator also expressed a preference to be able to explore and run a variety of descriptive analyses followed up with inferential statistics.
We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences. 
Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis.
While this is a valid way to explore data and generate new hypotheses, it is not suitable for hypothesis testing.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate. 
The well-established solution to this problem is to apply a correction for family-wise error (i.e., alpha correction). 
However, less clear-cut degrees of freedom such as observed in the present study can not be corrected for in a straightforward way. 
If uncorrected for, these degrees of freedom can nevertheless drastically inflate the false positive rate, even if different choices are highly correlated [@roettger2019researcher]. 
Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking; @john2012measuring; @simmons2011false], while null results remain unreported [@sterling1959publication; @rosenthal1979file]. 
Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.

@@

The current results point to important barriers to the successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [@vazire2017quality; @fidler2018reproducibility].
One of the suggested paths forward is for researchers to directly replicate previous studies more often [@open2015estimating; @camerer2018evaluating].
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
Beyond a replication crisis, quantitative disciplines are going through what has been called an "inference crisis" [@rotello2015more; @starns2019assessing].
As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility [see @campbell1975 for an overview of the concept].

@@

Finally, the present study focused on a particular phenomenon within the speech sciences using a speech production data set with very specific properties.
The generalizability of our findings to other disciplines, as well as to other sub-disciplines of the language sciences specifically, is, of course, limited.
We focused on quantitative analyses that require the operationalization of a multidimensional signal in an artificial elicitation situation (laboratory speech). 
While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals. 
This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods [@haven2019].
It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.

@@

In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis. 
When many different analysts have to analyze the same data set to answer the same research question, analysts differ in how they approach this task, leading to both different qualitative answers (i.e. is there evidence for a relationship or not) and different effect magnitudes. 
This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.
More specifically, what we find of particular relevance is the fact that commonly research proceeds based on publications from one research team at a time.
If we imagine a situation where any of the 46 teams could have been *the* team publishing a study on this topic, it is immediately clear that that single study is just a very limited view.
In light of this we want to stress that the field has to quickly move from one-off studies to collaborative approaches like the one employed here and to more frequent replication attempts for example by incentivizing replication through dedicated funding and editorial policies, among others.

### 2022-10-28 RR_manuscript/Draft_RR.tex

After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes \(\eta_i\).
The likelihood of \(\eta_i\) was assumed to correspond to a normal distribution \citep{knight2000}.
The analysis teams were entered as a group-level effect (i.e., \texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the frequentist literature).
The standard errors \(\text{se}_i\) were included as the standard deviation of \(\eta_i\) to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
The model did not incur any divergent transitions (\(\hat{R}\) was equal or lower than 1) and the estimated sample sizes were sufficient.
The code used to run the model can be found at \textless\textgreater.

@@

We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to follow the research protocol.
We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.

@@

The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0.1\) standard units and 95\% probability.
The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between 7.4 and 15.1 ms at 95\% credibility.
We interpret these values in more details in the Discussion section.

@@

Figure \ref{fig:plot-meta2}, panel C, displays the coefficients for all predictors alongside their 80\% and 95\% credible intervals.
The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
Neither analysts' prior beliefs in the phenomenon (\(\beta\) = 0.00, 95\% CrI = {[}-0.03, 0.03{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.03, 0.04{]}) seem to affect model estimates.
Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.05{]}).
Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.05, 95\% CrI = {[}0.02, 0.07{]}).

@@

Regardless of the cause of these systematic effects, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant prediction.
This conclusion is further supported by the fact that between-team variability was lower than between-model variability.
This is an important observation when put into context of the fact that most teams submitted many different models.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher, simmons2011false}.
One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): ``{[}T{]}he project's approach is too much top-down instead of bottom-up. {[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis.
While this is a valid way to explore data and generate new hypotheses, it is not suitable for hypothesis testing.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate.
The well-established solution to this problem is to apply a correction for family-wise error (i.e., alpha correction).
However, less clear-cut degrees of freedom such as observed in the present study can not be corrected for in a straightforward way.
If uncorrected for, these degrees of freedom can nevertheless drastically inflate the false positive rate, even if different choices are highly correlated \citep{roettger2019researcher}.
Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep{kerr1998harking, john2012measuring, simmons2011false}, while null results remain unreported \citep{sterling1959publication, rosenthal1979file}.
Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.

@@

The current results point to important barriers to the successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep{vazire2017quality, fidler2018reproducibility}.
One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep{open2015estimating, camerer2018evaluating}.
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility.

@@

Finally, the present study focused on a particular phenomenon within the speech sciences using a speech production data set with very specific properties.
The generalizability of our findings to other disciplines, as well as to other sub-disciplines of the language sciences specifically, is, of course, limited.
We focused on quantitative analyses that require the operationalization of a multidimensional signal in an artificial elicitation situation (laboratory speech).
While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods.
It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.

@@

In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis.
When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to both different qualitative answers (i.e.~is there evidence for a relationship or not) and vastly different effect magnitudes.
This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.

>>>>

After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor in each reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
The outcome variable was the set of standardized effect sizes \(\eta_i\).
The likelihood of \(\eta_i\) was assumed to correspond to a normal distribution \citep{knight2000}.
The analysis teams were entered as a group-level effect (i.e., \texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the frequentist literature).
The standard errors \(\text{se}_i\) were included as the standard deviation of \(\eta_i\) to fit a measurement-error model, as discussed above.
We used regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
The model did not incur any divergent transitions (\(\hat{R}\) was not greater than 1) and the estimated sample sizes were sufficient.
The code used to run the model can be found at \textless\textgreater.

@@

We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to follow the research protocol.
We also excluded any individual analysis that does not produce an outcome that could be interpreted as an answer to our primary question.
For a list of exlcusion criteria, see Section Descriptive statistics below.

@@

The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0\) to \(\pm 0.1\) standard units and 95\% probability.
The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between 7.4 and 15.1 ms at 95\% credibility.
We interpret these values in more details in the Discussion section.

@@

We have run a model as described in Section Analytic and researcher-related predictors affecting effect sizes above.
Figure \ref{fig:plot-meta2}, panel C, displays the coefficients for all predictors alongside their 80\% and 95\% credible intervals.
The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
Neither analysts' prior beliefs in the phenomenon (\(\beta\) = 0.00, 95\% CrI = {[}-0.03, 0.03{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.03, 0.04{]}) seem to affect model estimates.
Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.05{]}).
Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.05, 95\% CrI = {[}0.02, 0.07{]}).

@@

Regardless of the cause of these systematic effects, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant prediction.
This conclusion is further supported by the fact that between-team variability was lower than between-model variability.
This is an important observation when put into context of the fact that most teams submitted many different models.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher, simmons2011false}.
We of course are not arguing that exploratory analyses should not be employed.
Rather, we simply want to point out that if the theoretical underpinnings of the field were much clearer, different teams would have converged towards a limited set of analyses despite of a less specific research question.

In relation to this aspect, one team coordinator decided to drop out of the project because of its approach being too top-down.
The coordinator also expressed a preference to be able to explore and run a variety of descriptive analyses followed up with inferential statistics.
We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis.
While this is a valid way to explore data and generate new hypotheses, it is not suitable for hypothesis testing.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate.
The well-established solution to this problem is to apply a correction for family-wise error (i.e., alpha correction).
However, less clear-cut degrees of freedom such as observed in the present study can not be corrected for in a straightforward way.
If uncorrected for, these degrees of freedom can nevertheless drastically inflate the false positive rate, even if different choices are highly correlated \citep{roettger2019researcher}.
Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep{kerr1998harking, john2012measuring, simmons2011false}, while null results remain unreported \citep{sterling1959publication, rosenthal1979file}.
Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.

@@

The current results point to important barriers to the successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep{vazire2017quality, fidler2018reproducibility}.
One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep{open2015estimating, camerer2018evaluating}.
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility \citep[see][ for an overview of the concept]{campbell1975}.

@@

Finally, the present study focused on a particular phenomenon within the speech sciences using a speech production data set with very specific properties.
The generalizability of our findings to other disciplines, as well as to other sub-disciplines of the language sciences specifically, is, of course, limited.
We focused on quantitative analyses that require the operationalization of a multidimensional signal in an artificial elicitation situation (laboratory speech).
While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods \citep{haven2019}.
It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.

@@

In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis.
When many different analysts have to analyze the same data set to answer the same research question, analysts differ in how they approach this task, leading to both different qualitative answers (i.e.~is there evidence for a relationship or not) and different effect magnitudes.
This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.
More specifically, what we find of particular relevance is the fact that commonly research proceeds based on publications from one research team at a time.
If we imagine a situation where any of the 46 teams could have been \emph{the} team publishing a study on this topic, it is immediately clear that that single study is just a very limited view.
In light of this we want to stress that the field has to quickly move from one-off studies to collaborative approaches like the one employed here and to more frequent replication attempts for example by incentivizing replication through dedicated funding and editorial policies, among others.

### 2022-10-28 scripts/r/09_credit_taxonomy.Rmd

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE
  )

@@

```{r}
#| label: load-libs
library("googledrive")
library("xml2")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("forcats")
library("readr")
library("kableExtra")
```

@@

```{r}
#| label: identify-download
# give gargle permission
drive_auth(email = TRUE)

# Locate file, check ID
drive_find(n_max = 5, type = "spreadsheet")

# Search by id (just checking)
drive_get(id = "1lXmubF42sTCoOaECXGzo20GCFxX51MWFOKhX8euNtuA")

# Download to doc folder
drive_download(
  file = "MSA_tenzing_contribution", 
  path = "./data/CRediT/MSA_tenzing_contribution.csv", 
  type = "csv",
  overwrite = T
  )
```

@@

# Load data
all_data_temp <- read_csv("./data/CRediT/MSA_tenzing_contribution.csv") %>% 
  janitor::clean_names()

@@

cr_prep %>% 
  filter(is_initiating == 0) %>% 
  ggplot() +
  aes(y = initials, x = contributor_roles, alpha = val) +
    geom_point(size = 1.75, pch = 18, show.legend = F) +
    scale_x_discrete(labels = contributor_roles) + 
    scale_alpha_continuous(range = c(0.05, 1)) +
    labs(x = NULL, y = "Analysts",
         caption = "Contributor roles\nAuthor contributions based on CRediT taxonomy") +
    theme_minimal(base_size = 12, base_family = "Times") +
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15), 
      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, 
                                     size = rel(0.6)), 
      axis.text.y = element_text(size = rel(0.5))
    )

>>>>

```{r setup}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE
  )

@@

```{r}
#| label: load-libs
library(googlesheets4)
library("xml2")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("forcats")
library("readr")
library("kableExtra")
```

@@

```{r}
#| label: identify-download

all_data_temp <- read_sheet("1lXmubF42sTCoOaECXGzo20GCFxX51MWFOKhX8euNtuA") %>% 
  janitor::clean_names()

# Download to doc folder
write_csv(all_data_temp, "data/CRediT/MSA_tenzing_contribution.csv")
```

@@

@@

cr_prep %>% 
  filter(is_initiating == 0) %>% 
  ggplot() +
  aes(y = initials, x = contributor_roles, alpha = val) +
    geom_point(size = 1.75, pch = 18, show.legend = F) +
    scale_x_discrete(labels = contributor_roles) + 
    scale_alpha_continuous(range = c(0.05, 1)) +
    labs(x = NULL, y = "Analysts",
         caption = "Contributor roles\nAuthor contributions based on CRediT taxonomy") +
    theme_light(base_size = 12, base_family = "Times") +
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15), 
      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, 
                                     size = rel(0.6)), 
      axis.text.y = element_text(size = rel(0.5))
    )

ggsave("figs/credit-taxonomy.png", width = 14, height = 10)
```
